Databases are an effective and efficient method for storage and access of mass-spectrometry data

### 2025-02-28 manuscript/manuscript.Rmd
Tidying shell commands

Files were downloaded as .raw. mzML, mz5, and mzMLb were all natively supported by Proteowizard's `msconvert` software (version 3.0.25009) while MZA (v1.24.11.16) and mzDB (v0.9.10_build20170802) had separate extensions to this executable enabling their own conversion. MzTree and mzMD were converted via their GUI which did not have release or versioning information available but were downloaded from Github (https://github.com/optimusmoose/MZTree and https://github.com/yrm9837/mzMD-java, respectively) and built via Maven (v3.9.9) for Java (v21.0.6). SQL databases were built using Python 3.11.11 with SQLite (v3.48.0) via the Python sqlite3 package (v2.6.0), DuckDB via the duckdb package (v1.1.3), and Parquet files via the pyarrow package (v19.0.0). We were additionally able to download and install

@@

cd java_things
curl -O https://dlcdn.apache.org/maven/maven-3/3.9.9/binaries/apache-maven-3.9.9-bin.zip
tar -xf apache-maven-3.9.9-bin.zip
git clone https://github.com/optimusmoose/MZTree.git
cd MZTree
cd msDataServer
C:\Users\willi\Documents\mzsql\java_things\apache-maven-3.9.9\bin\mvn package
java -Dsun.java2d.d3d=false -Dsun.java2d.opengl=false -jar target\msDataServer-1.0.jar
(manually) open mztree file in port 4568

git clone https://github.com/yrm9837/mzMD-java.git
cd mzMD-java
C:\Users\willi\Documents\mzsql\java_things\apache-maven-3.9.9\bin\mvn package
java -Dsun.java2d.d3d=false -Dsun.java2d.opengl=false -jar target\msDataServer-1.0.jar
(manually) open mzmd file in port 4567
cd ..

@@

# After adding msconvert, raw2mzdb, and mza executables to PATH:
msconvert 20220921_LEAP-POS_BL01.raw --filter "peakPicking true 1-"
msconvert 20220921_LEAP-POS_BL01.raw --mzMLb --filter "peakPicking true 1-"
msconvert 20220921_LEAP-POS_BL01.raw --mz5 --filter "peakPicking true 1-"
raw2mzDB -i 20220921_LEAP-POS_BL01.raw  -c 1-2 --safeMode
mza -file 20220921_LEAP-POS_BL01.raw
```

>>>>

Files were downloaded as .raw. mzML, mz5, and mzMLb were all natively supported by Proteowizard's `msconvert` software (version 3.0.25009) while MZA (v1.24.11.16) and mzDB (v0.9.10_build20170802) had separate extensions to this executable enabling their own conversion. MzTree and mzMD were converted via their GUI which did not have release or versioning information available but were downloaded from Github (https://github.com/optimusmoose/MZTree and https://github.com/yrm9837/mzMD-java, respectively) and built via Maven (v3.9.9) for Java (v21.0.6). SQL databases were built using Python 3.11.11 with SQLite (v3.48.0) via the Python sqlite3 package (v2.6.0), DuckDB via the duckdb package (v1.1.3), and Parquet files via the pyarrow package (v19.0.0). We were additionally able to download and install []

@@

cd java_things
curl -O https://dlcdn.apache.org/maven/maven-3/3.9.9/binaries/apache-maven-3.9.9-bin.zip
tar -xf apache-maven-3.9.9-bin.zip
git clone https://github.com/optimusmoose/MZTree.git
cd MZTree
cd msDataServer
C:\Users\willi\Documents\mzsql\java_things\apache-maven-3.9.9\bin\mvn package
java -Dsun.java2d.d3d=false -Dsun.java2d.opengl=false -jar java_things\MZTree\msDataServer\target\msDataServer-1.0.jar
(manually) open mztree file in port 4568

git clone https://github.com/yrm9837/mzMD-java.git
cd mzMD-java
C:\Users\willi\Documents\mzsql\java_things\apache-maven-3.9.9\bin\mvn package
java -Dsun.java2d.d3d=false -Dsun.java2d.opengl=false -jar java_things\mzMD-java\target\msDataServer-1.0.jar
(manually) open mzmd file in port 4567

@@

# After adding msconvert, raw2mzdb, and mza executables to PATH:
msconvert 20220923_LEAP-POS_QC04.raw --filter "peakPicking true 1-"
msconvert 20220923_LEAP-POS_QC04.raw --mzMLb --filter "peakPicking true 1-"
msconvert 20220923_LEAP-POS_QC04.raw --mz5 --filter "peakPicking true 1-"
# Needs full path or it crashes on startup?
"C:\Program Files\ProteoWizard\raw2mzDB_0.9.10_build20170802\raw2mzDB.exe" -i 20220923_LEAP-POS_QC04.raw  -c 1-2 --safeMode
mza -file 20220923_LEAP-POS_QC04.raw
```
